% a. General: [Alireza]
% ยง Mention the verify function and security game etc
\section{Digital Signatures}\label{sec:signatures}


A digital signature is an asymmetric cryptographic primitive for verifying the authenticity of digital messages or documents \cite{goldwasser1983strong,goldwasser1988digital,bellare1988sign,rompel1990one,goldwasser2008lecturenotes}. A valid signature on a message gives a recipient trust in that the message was authored by a sender known to the recipient. Digital signatures are commonly used for financial transactions, software distribution, and to detect forgery or tampering in communication.

Assuming that the private key remains secret, digital signatures are designed to be inherently \textit{resistant to forging}, making it computationally infeasible to generate a valid signature on behalf of a party without knowing that party's private key. They may also provide \textit{non-repudiation}, thus signer cannot successfully claim they did not sign a message. Digitally signed messages may be anything that can be represented as a bit-string, e.g., cryptocurrency transactions, electronic mail, or messages sent as part of cryptographic protocols.

We generalize digital signature schemes in Functionality \ref{alg:f_signature}:

\input{src/algorithms/signatures/F_signature}

The security of digital signature schemes is filled with nuances. In general, the security of a digital signature scheme is defined by a security game between a challenger and an adversary. Based on the capabilities granted to the adversary, we distinguish three basic attacks (more details in \cite{goldwasser1983strong}):
\begin{itemize}
    \item \textit{Key-Only Attack (KOA)}: the adversary knows only the public key of the signer, thus it can verify signatures of messages given to him.
    \item \textit{Known Signature Attack (KSA)}: the adversary is given the public key of the signer and message/signature pairs from a legal signer.
    \item \textit{Chosen Message Attack (CMA)}: The adversary is also given access to a signing oracle, a black-box that signs any message of the adversary's choice. Out of the three, this is the most powerful adversary and is considered the only realistic notion for many real-world scenarios.
\end{itemize}

\noindent The adversary's goal in the security game may be:
\begin{itemize}
    \item \textit{Existential Forgery (EF)}: succeed in forging the signature of one message, not necessarily of his choice.
    \item \textit{Selective Forgery (SF)}: succeed in forging the signature of some message of his choice.
    \item \textit{Universal Forgery (UF)}: succeeds in forging the signature of any message.
    \item \textit{Total Break}: succeed in computing the signer's secret key.
\end{itemize}

The signature scheme is then considered secure if the adversary's probability of winning the game for a given goal and attack is negligible. We refer the avid reader to \cite{goldwasser2008lecturenotes} for more formal definitions.

There exist many different digital signature schemes, each with their own performance characteristics. In this section, we focus our attention to the most common signature schemes used in blockchain protocols: ECDSA~\cite{ecdsa_rfc6979}, Schnorr / EdDSA~\cite{eddsa_rfc8032}, and BLS~\cite{irtf_bls_signature_05}. These three schemes are proven secure under the \textit{UF-CMA} security definition\footnote{Some signature schemes such as Schnorr / EdDSA go even beyond, as they constitute \textit{zero knowledge proofs of knowledge} of the secret key.}, the strongest combination out of the classical security notions presented above. All these schemes are based on elliptic curve cryptography, for specifically chosen curves.

\input{src/sections/3_signatures/3_ecdsa}
\input{src/sections/3_signatures/3_schnorr}
\input{src/sections/3_signatures/3_bls}