\documentclass{article}

%------------------------------HEADERS & VERSION-------------------------------%
    \input{src/headers/spec_header}
    \input{src/headers/spec_notation}

    \newcommand{\specversion}{Version 0.9}

%-----------------------------------TITLE--------------------------------------%
    \title{Cryptographic Specification of Bron.xyz\\(\specversion)}
    \author{Alireza Rafiei, Alberto Ibarrondo, Mateusz Kramarczyk \\ Hoang Ong}
    \date{\today}

\begin{document}

%-------------------------------TITLE PAGE & ToC-------------------------------%
\maketitle
\begin{abstract}
    This document contains the specification of the cryptographic protocols and primitives that serve as base for the Multi-Party Computation (MPC) platform of \href{https://bron.xyz}{Bron}. This specification serves a reference for the implementation of all the techniques described in it.

    As a custody solutions provider, Bron's main objective with its MPC platform is to provide state-of-the-art protection for digital assets (e.g., cryptocurrencies) while allowing its clients to operate with them with the utmost security guarantees. To this end, we target distributed variants of Elliptic-Curve (EC) signature schemes commonly used to sign transactions in popular blockchains (ECDSA, Schnorr/EdDSA, BLS). We select MPC protocols that are proven secure against malicious adversaries in a $t$-out-of-$n$ threshold setting: $n$ parties generate and hold shares of the underlying private key, and any subset of $t$ parties can sign a transaction. This threat model tolerates up to $t-1$ static corruptions throughout the protocol execution. Our chosen distributed signing protocols are:
    \begin{itemize}
        \item DKLs23~\cite{DKLS23} and Lindell17~\cite{lindell17}\footnote{The latter only supports $t=2$, for any $n$.} for threshold ECDSA.
        \item Lindell22~\cite{L22} for threshold Schnorr.
    \end{itemize}
    We also specify the cryptographic primitives required by these protocols, including Distributed Key Generation (DKG), Oblivious Transfer (OT), proofs of knowledge (PoK), Cryptographically-Secure Pseudo-Random Number Generation (CSPRNG) and other general primitives.
\end{abstract}
\newpage
\tableofcontents
\clearpage

%----------------------------------SECTIONS------------------------------------%


\input{src/sections/1_introduction/1_introduction}
\clearpage

\input{src/sections/2_preliminaries/2_preliminaries}
\clearpage

\input{src/sections/3_signatures/3_signatures}
\clearpage

\input{src/sections/4_threshold_signatures/4_threshold_signatures}
\clearpage

\input{src/sections/5_tecdsa/5_tecdsa}
\clearpage

\input{src/sections/6_tschnorr/6_tschnorr}
\clearpage

\input{src/sections/7_tbls/7_tbls}
\clearpage

\bibliographystyle{alpha}
\bibliography{src/bib/tecdsa.bib,src/bib/refresh.bib,src/bib/primitives.bib,src/bib/tschnorr.bib,src/bib/various.bib,src/bib/tbls.bib}

\appendix
\input{src/sections/appendix/appendix}

\end{document}
